---
title: "Deliverable 2"
author: "Garrett Hawes, Bart Ciastkowski, Ricky Lobel"
date: "`r Sys.Date()`"
output: 
  html_document: 
    code_folding: show
    css: includes/styles.css
    fig_caption: yes
    highlight: tango
    includes:
      after_body: includes/footer.html
      before_body: includes/header.html
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_chunk$set(cache = TRUE)
knitr::opts_chunk$set(warning = FALSE)
library("conflicted")
library("here")
library("arsenal")
library("tidyverse")
library("knitr")
library("kableExtra")
library("ggExtra")
library("ggthemes")
library("GGally")
library("ggmap")
library("plyr")
library("stringr")
library("stringi")
library("PerformanceAnalytics")
library('sentimentr')
library("tm")
library("SnowballC")
library("RColorBrewer")
library("wordcloud")
conflict_prefer("mutate", "dplyr")
conflict_prefer("summarize", "dplyr")

```

# Load Data 

```{r warning=FALSE}
wine_data <-
  read.csv(here::here("data", "input", "winemag-data-130k-v2.csv"))
colors <- read.csv(here::here("data", "input", "wine-colors.csv"))
twitter_stats <- read.csv(here::here("data", "input", "twitter-data.csv"))

# Add color
# wine_data_with_color <- left_join(wine_data, colors, by = "variety")
wine_data <- dplyr::left_join(wine_data, colors, by = "variety")

# Add in twitter stats 

wine_data <- dplyr::left_join(wine_data, twitter_stats, by = "taster_twitter_handle")

```



# Clean

## Functions
```{r fxns}
.clean_text <- function(x) {
  x <- stringi::stri_trans_general(x, "Latin-ASCII")
  x <- str_replace_all(x, "[^A-Za-z]", " ")
  x <- tolower(x)
  x <- str_squish(x)
  return(x)
}

.clean_fct_text <- function(x) {
  x <- as.character(x)
  .clean_text(x)
  return(x)
}
```

## Color Revalue

```{r color-rvl}
wine_data <-
  wine_data %>% dplyr::mutate(color = revalue(
    wine_data$color,
    c(
      "O" = "Other",
      "R" = "Red",
      "W" = "White",
      "SW" = "Sparkling White"
    )
  ))
```

## Apply Cleaning
Apply the cleaning strategies from above
```{r apply-clean}
wine_data <-
  wine_data %>% dplyr::mutate(
    country = as.character(country),
    variety = as.character(variety),
    taster_name = as.character(taster_name),
    title = as.character(title),
    color_lump = fct_lump(color, n = 2), 
    province_lump = fct_lump(wine_data$province, n = 10),
    country_lump = fct_lump(wine_data$country, n = 10)
  ) %>%
  dplyr::filter (country != "" &
            variety != "" & taster_name != "") %>% drop_na(price) 
```

# Feature Generation

## Points Categories
 Turn score into categories per https://www.winespectator.com/articles/scoring-scale
```{r points-cat}
wine_data <-
  wine_data  %>% dplyr::mutate(point_cat = cut(
    wine_data$points,
    breaks = c(0, 74, 79, 84, 89, 94, 100),
    labels = c(
      "Not Recomended",
      "Mediocre",
      "Good",
      "Very good",
      "Outstanding",
      "Classic"
    )
  ))
```

## Price Categories
 Turn score into categories per https://www.winespectator.com/articles/scoring-scale
```{r price-cat}
wine_data <-
  wine_data  %>% 
  dplyr::mutate(price_cat = cut(
                            price,
                            breaks = c(0, 4, 12, 50, 200, 750, 3000),
                            labels = c( "Budget ($0-4)", 
                                        "Every Day ($5-12)", 
                                        "Premium ($13-50)", 
                                        "Ultra Premium ($51-200)", 
                                        "Luxury ($201-750)", 
                                        "What the fuck is wrong with you? ($751+)" )))
```

## Title Features {.tabset .tabset-fade .tabset-pills}

### Legth

```{r title-length}
wine_data <-
  wine_data %>% dplyr::mutate(title_length =  nchar(as.character(wine_data$title)))
```

### Has Accent(s)
Has accents presuming the american market might pay more ... or less for wines that sound exotic.
```{r title-accents}
wine_data <-
  wine_data %>% dplyr::mutate(title_has_accents = 
                                (title != stringi::stri_trans_general(title, "Latin-ASCII")))
```

### Title Sentiment Analysis and Word Count

```{r title-sentiment}
 wine_data <- 
   wine_data %>% dplyr::mutate(title_no_accents = stringi::stri_trans_general(title, "Latin-ASCII"))

s <- sentiment_by(wine_data$title_no_accents)

qplot(s$ave_sentiment, geom="histogram",binwidth=0.2,main="Wine Title Sentiment Histogram")

wine_data <- wine_data %>% dplyr::mutate(title_sentement = s$ave_sentiment, 
                                         title_word_count = s$word_count)
```

## Designation column {.tabset .tabset-fade .tabset-pills}

### Clean text

```{r}
wine_data <- wine_data %>% dplyr::mutate(designation = .clean_text(designation))
wine_designations_word_cloud <- wine_data
```
 
### Identify Possible Groups

```{r}
wine_designations_word_cloud <-
  wine_designations_word_cloud %>% mutate(designation = str_replace_all(designation, "([Rr].serv.)", "Reserve"))

## Calculate Corpus

wineDesignation.Corpus <-
Corpus(VectorSource(wine_designations_word_cloud$designation))

#Data Cleaning and Wrangling

wineDesignation.clean <- tm_map(wineDesignation.Corpus,
                                 PlainTextDocument)
wineDesignation.clean <-
  tm_map(wineDesignation.Corpus, tolower)
wineDesignation.clean <-
  tm_map(wineDesignation.Corpus, removeNumbers)
wineDesignation.clean <-
  tm_map(wineDesignation.Corpus, removeWords, stopwords("english"))
wineDesignation.clean <-
  tm_map(wineDesignation.Corpus, removePunctuation)
wineDesignation.clean <-
  tm_map(wineDesignation.Corpus, stripWhitespace)

wordcloud(words = wineDesignation.clean, min.freq = 2,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"))
```


### Group
```{r}
# List of regular expressions to match

patterns <-
  c(
    ".*([Rr].serv).*",
    ".*extra dry.*",
    ".*(dry|trocken).*",
    ".*brut.*",
    ".*(estate|grand|casa).*",
    ".*single.*",
    ".*(klassik|classic|tradition|vintage).*",
    ".*rose.*",
    ".*barrel s.*",
    ".*(old v|vieilles).*",
    ".*(vineyard|ranch|alpha|branco|broquel).*",
    ".*(barrel|crianza|cuve).*",
    ".*unoaked.*",
    ".*cuve prestige.*",
    ".*(blanc|white|bianco).*",
    ".*(red|tinto|bussia).*",
    ".*(nouveau|proprietary|signature|selec|premier).*",
    ".*lot.*",
    ".*late.*",
    ".*(oak|roble).*",
    ".*(organic|cannubi).*",
    ".*(port|colheita).*",
    ".*(collection|premium|prestige|limited).*",
    ".*clone.*",
    ".*(block|bin).*",
    "^$"
  )

# Values to replace above patterns with

replacements <-
  c(
    "Reserve",
    "Extra Dry",
    "Dry",
    "Brut",
    "Estate",
    "Single Vineyard",
    "Classic Vintage",
    "Rose",
    "Barrel Sample",
    "Old Vine",
    "Some Vineyard",
    "Barrel",
    "UnOaked",
    "Finest Champagne",
    "White",
    "Red",
    "Signature",
    "Lot",
    "Late Harvest",
    "Oak",
    "Organic",
    "Port",
    "Premium",
    "Clone",
    "Block",
    "No Designation"
  )

# This is so that we can use the replacements object in str_replace_all 
# rather than a single pattern/replacement

names(replacements) <- patterns

wine_data <-
  wine_data %>% dplyr::mutate(designation = str_replace_all(designation, replacements)) %>% 
  dplyr::mutate(designation = as.factor(designation))
```

## Lump Varieties
```{r}
.append_color_to_factor <- function(variety, color) {
  variety = as.character(variety)
  variety = paste(variety, color)
  return(variety)
}

red <-
  wine_data %>% dplyr::filter(color_lump == "Red") %>%
  dplyr::mutate(variety_lump = fct_lump(variety, n = 5)) %>%
  dplyr::mutate(variety_lump = .append_color_to_factor(variety_lump, "(R)"))
white <-
  wine_data %>% dplyr::filter(color_lump == "White") %>%
  dplyr::mutate(variety_lump = fct_lump(variety, n = 5)) %>%
  dplyr::mutate(variety_lump = .append_color_to_factor(variety_lump, "(W)"))
other <-
  wine_data %>% dplyr::filter(color_lump == "Other") %>%
  dplyr::mutate(variety_lump = "Other")

wine_data_bind <- do.call("rbind", list(red, white, other))

wine_data <-
  wine_data_bind %>% dplyr::mutate(variety_lump = factor(variety_lump))
```

## Lump Other Factors
```{r}
wine_data <-
  wine_data %>% dplyr::filter(as.character(taster_twitter_handle) != "") %>% dplyr::mutate(
    taster_name_lump = fct_lump(taster_name, n = 5),
    taster_twitter_lump = fct_lump(taster_twitter_handle, n = 5),
    designation_lump = fct_lump(designation, n = 10),
    country_lump = fct_lump(country, n = 10),
    variety_lump = fct_lump(variety, n = 10)
  )
```

## Add reviewer stats
```{r}
wine_data <- wine_data %>%
  dplyr::group_by(taster_name) %>%
  dplyr::mutate(taster_avg_points = mean(points),
                   taster_review_count = n()) %>% dplyr::ungroup()
```

## Ad ID column
```{r}
wine_data <- tibble::rowid_to_column(wine_data, "ID")
```

## Drop unused point category factors 
```{r message=FALSE, warning=FALSE, results='hide'}
setdiff(levels(wine_data$point_cat), wine_data$point_cat)
fct_drop(wine_data$point_cat)
```

## Drop unneeded columns 
```{r}
wine_data_clean <-
  wine_data %>%
  dplyr::select(
    ID,
    price,
    country,
    variety,
    points,
    point_cat,
    title_length,
    title_has_accents,
    variety_lump,
    designation_lump,
    taster_name_lump,
    taster_twitter_lump,
    taster_gender,
    taster_avg_points,
    taster_review_count,
    taster_n_tweets,
    color_lump,
    country_lump,
    province_lump,
    price_cat,
    title_word_count,
    title_sentement
  ) %>% droplevels()
```

## Unused columns
```{r}
setdiff(names(wine_data), names(wine_data_clean))
```

# Summary Statistics {.tabset .tabset-fade .tabset-pills}

## Numeric Columns
```{r numeric-simple, results="asis"}
table_numeric <-
  tableby(~ ., data = wine_data_clean %>% 
            select_if(is.numeric))
summary(table_numeric, title = "Wine Data by Price - Numeric Columns")
```

## Factor Columns 
```{r factors, results="asis"}
table_factor <-
  tableby(~ ., data = wine_data_clean %>% 
            select_if(is.factor))
summary(table_factor, title = "Wine Data by Price - Factor Columns")
```


## Complete
```{r summary, results="asis"}
table_complete <-
  tableby(price_cat ~ ., data = wine_data_clean %>%
    select(
      -c(ID, country, variety)
    ))
summary(table_complete, title = "Wine Data by Price Group")

```


# Plots 

## Maps {.tabset .tabset-fade .tabset-pills}

```{r map, message=FALSE}
world_map <- map_data("world")
world_map <-
  world_map %>% dplyr::mutate(region = ifelse(region == "USA", "US", region))
world_map <- world_map %>% dplyr::mutate(country = region)

wine_map_DF <-
  wine_data_clean  %>% dplyr::mutate(country = as.character(country)) %>%
  dplyr::filter (country != "England" &
            country != "US-France" &
            country != "")

# Generate Summary
wmap <-
  wine_data_clean %>%
  dplyr::group_by(country) %>%
  dplyr::summarize(
    point_min = min(points, na.rm = TRUE),
    point_avg = mean(points, na.rm = TRUE),
    point_max = max(points, na.rm = TRUE),
    price_min = min(price, na.rm = TRUE),
    price_avg = mean(price, na.rm = TRUE),
    price_max = max(price, na.rm = TRUE)
  ) %>%
  dplyr::select(
    c(
      "country",
      "point_min",
      "point_avg",
      "point_max",
      "price_min",
      "price_avg",
      "price_max"
    )
  )
# Create data frame with bounderies and values
wine_country_map <- right_join(wmap, world_map, by = "country")

#scale_fill_viridis_c(option = "C", limits = c(80, 100)) + theme_map() + ggtitle(title)

.map_from_attribute <- function(att, title) {
  return(
    ggplot(wine_country_map, aes_string(map_id = "country", fill = att)) +
      geom_map(map = wine_country_map,  color = "white") +
      expand_limits(x = wine_country_map$long, y = wine_country_map$lat) +
      scale_fill_viridis_c(option = "C") + theme_map() + ggtitle(title) + 
      theme(plot.title = element_text(hjust = 0.5)) + 
      theme(plot.title = element_text(size=20)) +
      theme(legend.title = element_blank()) 
  )
}
```
### Points - Min
```{r}
.map_from_attribute("point_min", "Minimum Points")
```

### Points - Average
```{r}
.map_from_attribute("point_avg", "Average Points")
```

### Points - Max
```{r}
.map_from_attribute("point_max", "Maximum Points") 
```

### Price - Min
```{r}
.map_from_attribute("price_min", "Minimum Price") 
```

### Price - Average
```{r}
.map_from_attribute("price_avg", "Average Price") 
```

### Price - Max
```{r}
.map_from_attribute("price_max", "Maximum Price") 
```

## Corelation
```{r plot1, fig.height=9, fig.width=10, message=FALSE}
ggpairs(wine_data_clean, columns = c(2,5,7, 14, 16), ggplot2::aes(colour=color_lump))
```

## Price v Points

```{r plot2, message=FALSE}
p <- ggplot(wine_data_clean, aes(points, price, color = point_cat)) + 
      geom_point() + 
      theme_clean() + 
      labs(title = "Price vs Points")
p1 <- ggMarginal(p, type="histogram", fill="slateblue") 
p1 
```

## Box Plot
```{r plot3, fig.height=8, fig.width=10, message=FALSE}
wine_data_clean %>% ggplot(aes(x = reorder(color_lump, points), y = points, fill = color_lump)) + 
  geom_boxplot() + 
  xlab("Color") + 
  theme_clean() + 
  theme(legend.position = "none") + 
  ggtitle("Wine Score vs color. Faceted by Gender and presence of accents in title") + facet_wrap(~ country_lump)
```

## Score v log(price) faceted by Gender
```{r plot4, message=FALSE}
ggplot(wine_data_clean, aes(log(price), points, color = point_cat)) + 
  geom_point() + 
  theme_fivethirtyeight() + 
  labs(title = "Score vs log of Price") + 
  facet_wrap(~ taster_gender)
```

## log(price) v log(points) by Country
```{r plot5, message=FALSE}
ggplot(wine_data_clean, aes(log(price), log(points), color = point_cat)) + 
  geom_point() + 
  theme_fivethirtyeight() + 
  labs(title = "Score vs log of Price") + 
  facet_wrap(~ country_lump)
```

## Country v Price by rating category
```{r plot6, fig.height=6, fig.width=8, message=FALSE, warning=FALSE, paged.print=TRUE}
ggplot(wine_data_clean, aes(x = price, y = country_lump, color = point_cat)) +
  geom_jitter(alpha=1/2) + ggtitle("Price and Country Colored by Point_Cat")
```


## Country v log(Price) by rating category

```{r plot7, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, paged.print=TRUE}
ggplot(wine_data_clean, aes(x = log(price), y = country_lump, color = point_cat)) +
  geom_jitter(alpha=1/2) + ggtitle("log(Price) and Country Colored by Point_Cat")
```

## Taster Tweets v log(Price)
```{r plot8, fig.height=5, fig.width=8, message=FALSE, warning=FALSE, paged.print=TRUE}
  ggplot(wine_data_clean, aes(x = log(price), y = taster_n_tweets, color = point_cat)) +
  geom_jitter(alpha=1/2) + ggtitle("log(Price) and Country Colored by Point_Cat")
```



